Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-05-25 tex/test-WW-type-00v-PS.tex
alexei
math

We present calculations of $g_2(x)_{WW}$ in Fig.~\ref{Fig:g2}.
How well does the WW approximation describe data if we allow for a
theoretical ``uncertainty band'' of about $40\,\%$ as deduced in 
\cite{Accardi:2009au}? To investigate this question, 
we split this uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
$\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
and estimate the impact of this uncertainty as 
\be\label{Eq:g2-in-WW-model-violation}
    g_2(x)_{\rm WW} = (1\pm\varepsilon_1)\frac{ d\;}{ d x}\;\Biggl[
    x\int_x^1\frac{ d y}{y} \,\biggl(
    \frac12\sum_ae_a^2\,g_1^a(y(1\pm\varepsilon_2))\biggr)\Biggr]\,.
\ee
The effect of $\varepsilon_1$ is to change the magnitude
of $g_2(x)_{\rm WW}$, $\varepsilon_2$ varies the position of its zero.
The $x$--dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
the highest measured $x$--bin.
The good agreement of $g_2(x)_{\rm WW}$ with data is encouraging,
and in line with theory predictions \cite{Balla:1997hf}.
Our estimate with the splitted uncertainties 
$\varepsilon_{1,2}$ may overestimate in certain $x$--bins the 
$40\,\%$--``uncertainty band'' estimated in \cite{Accardi:2009au}. 
This however helps us to display a conservative estimate of possible 
uncertainties. 
We conclude that the WW--approximation works reasonably well
possibly except for very small $x$ at HERMES, see Fig.~\ref{Fig:g2}.

@@

The Kotzinian-Mulders function $h^{\perp q}_{1L}$ in conjuction with 
the Boer-Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjuction 
with the Sivers function obey the positivity bounds 
\cite{Bacchetta:1999kz}
\begin{subequations}\ba
	\frac{\kperp^2}{4M_N^2}\;(f_{1}^{q}(x,\kperp^2))^2 
	- (h^{\perp(1)q}_{1L}(x,\kperp^2))^2 
	- (h_{1}^{\perp(1)q}(x,\kperp^2))^2
	& \ge & 0\,, \label{eq:positivity}\\
	\frac{\kperp^2}{4M_N^2}\;(f_{1}^{q}(x,\kperp^2))^2 
	- (f_{1T}^{\perp(1)q}(x,\kperp^2))^2
	- (g^{\perp(1)q}_{1T}(x,\kperp^2))^2 
	& \ge & 0\,. \label{eq:positivity1}
\ea\end{subequations}
The inequalities provide a non-trivial test of our approach.
The inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) 
must be strictly satisfied by the {\it exact} leading--order QCD 
expressions for the TMDs.  
(For PDFs it is known that positivity can be preserved in some 
schemes but violated in other schemes. For TMDs not much is 
known about positivity conditions beyond leading order.)
However, here we do not deal with exact TMDs but (i) we invoked 
strong model assumptions (WW-type approximations for $g^{\perp q}_{1T}$ 
and $h^{\perp q}_{1L}$ and Gauss Ansatz for all TMDs), and (ii) we deal 
with first extractions which have sizable uncertainties including 
poorly controlled systematic uncertainties.
Therefore, considering that we deal with approximations 
(WW-type, Gauss) and considering the current state of TMD-extractions, 
the inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) constitute
a challenging test for the approach.

>>>>

We present calculations of $g_2(x)_{WW}$ in Fig.~\ref{Fig:g2}.
How well does the WW approximation describe data if we allow for a
theoretical ``uncertainty band'' of about $40\,\%$ as deduced in Ref.~\cite{Accardi:2009au}? To investigate this question, 
we split this uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
$\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
and estimate the impact of this uncertainty as 
\be\label{Eq:g2-in-WW-model-violation}
    g_2(x)_{\rm WW} = (1\pm\varepsilon_1)\frac{ d\;}{ d x}\;\Biggl[
    x\int_x^1\frac{ d y}{y} \,\biggl(
    \frac12\sum_ae_a^2\,g_1^a(y(1\pm\varepsilon_2))\biggr)\Biggr]\,.
\ee
The effect of $\varepsilon_1$ is to change the magnitude
of $g_2(x)_{\rm WW}$, $\varepsilon_2$ varies the position of its zero.
The $x$--dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
the highest measured $x$--bin.
The good agreement of $g_2(x)_{\rm WW}$ with data is encouraging,
and in line with theory predictions \cite{Balla:1997hf}.
Our estimate with the splitted uncertainties 
$\varepsilon_{1,2}$ may overestimate in certain $x$--bins the 
$40\,\%$--``uncertainty band'' estimated in \cite{Accardi:2009au}. 
This however helps us to display a conservative estimate of possible 
uncertainties. 
We conclude that the WW--approximation works reasonably well
possibly except for very small $x$ at HERMES, see Fig.~\ref{Fig:g2}.

@@

The Kotzinian-Mulders function $h^{\perp q}_{1L}$ in conjuction with 
the Boer-Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjuction 
with the Sivers function obey the positivity bounds 
\cite{Bacchetta:1999kz}
\begin{subequations}\ba
	\frac{\kperp^2}{4M_N^2}\;\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
	- (h^{\perp(1)q}_{1L}(x,\kperp^2))^2 
	- (h_{1}^{\perp(1)q}(x,\kperp^2))^2
	& \ge & 0\,, \label{eq:positivity}\\
	\frac{\kperp^2}{4M_N^2}\;\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
	- (f_{1T}^{\perp(1)q}(x,\kperp^2))^2
	- (g^{\perp(1)q}_{1T}(x,\kperp^2))^2 
	& \ge & 0\,, \label{eq:positivity1}
\ea\end{subequations}
where $f^{(1)}(x,\kperp^2) \equiv \frac{\kperp^2}{2M_N^2} f(x,\kperp^2)$.
The inequalities provide a non-trivial test of our approach.
The inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) 
must be strictly satisfied by the {\it exact} leading--order QCD 
expressions for the TMDs.  
(For PDFs it is known that positivity can be preserved in some 
schemes but violated in other schemes. For TMDs not much is 
known about positivity conditions beyond leading order.)
However, here we do not deal with exact TMDs but (i) we invoked 
strong model assumptions (WW-type approximations for $g^{\perp q}_{1T}$ 
and $h^{\perp q}_{1L}$ and Gauss Ansatz for all TMDs), and (ii) we deal 
with first extractions which have sizable uncertainties including 
poorly controlled systematic uncertainties.
Therefore, considering that we deal with approximations 
(WW-type, Gauss) and considering the current state of TMD-extractions, 
the inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) constitute
a challenging test for the approach.
